Array

### 2014-01-13 DOCUMENTATION/AdvancedTypes.tex
Fixed the rule to support array and added an example in coverage.sh

\begin{align*}
\lefteqn{\trad{n}{ArrayItem} \isdef} \\
&  \LET p_1 \sep v_1 \sep t_1  = \trad{n.base}{Exp}  \IN \\
&  \LET p_2 \sep v_2 \sep t_2  = \trad{n.indices}{\ListOf{Exp}}  \IN \\
&  \LET v =  \variable \AND  t = \trad{\B{n.type}}{Type}  \IN \\
&  \llvm{"\PH{p_1} \PH{p_2} \PH{v} =  getelementptr \PH{t_1}, \PH{v_1}, i32 0 \ListOf{(,\PH{t_2} \PH{v_2})}\nl"}  \sep v \sep t\\
\end{align*}

>>>>

\begin{align*}
\lefteqn{\trad{n}{ArrayItem} \isdef} \\
&  \LET p_1 \sep v_1 \sep t_1  = \trad{n.base}{Exp}  \IN \\
&  \LET r \sep p_2  = \trad{n.indices}{LRExp}  \IN \\
&  \LET v =  \variable \AND  t = \trad{\B{n.type}}{Type}  \IN \\
&  \llvm{"\PH{p_1} \PH{p_2} \PH{v} =  getelementptr \PH{t_1}, \PH{v_1}, i32 0 \PH{r}\nl"}  \sep v \sep t\\
\end{align*}

A list of type and variable is generated by the following rule.
%TODO: check this rule with David

\begin{align*}
&\trad{n}{LRExp} \isdef \LET p \sep v \sep t  = \trad{n}{Exp}  \IN  \llvm{",\PH{t} \PH{v} "} \sep p\\
&\trad{n l}{LRExp} \isdef \LET r_1 \sep p_1 = \trad{n}{LRExp} \AND 
 \LET r_2 \sep p_2 = \trad{l}{LRExp} \IN\\
& \quad  \llvm{"\PH{r_1} \PH{r_2}"} \sep \llvm{"\PH{p_1} \PH{p_2}"}\\
\end{align*}
